%
% Halaman Abstract
%
% @author  Andreas Febrian
% @version 1.00
%

%\chapter*{Abstract}
\setstretch{1}
\vspace*{0.2cm}
{
%    \begingroup
    \singlespacing
	\setlength{\parindent}{0pt}
	
	\begin{tabular}{@{}l l p{10cm}}
		Name&: & \penulis \\
		Study Program&: & \program \\
		Title&: & \judulInggris \\
		Supervisor&: & \pembimbing \\
	\end{tabular}

	\bigskip
	\bigskip
The thesis completion process at the Department of Computer Engineering, Universitas Indonesia, faces dual challenges: inefficiencies in the semi-manual administrative workflow and low student compliance with standardized writing formats. 
This research aims to design, build, and evaluate an integrated solution named D'Office, which consists of a web-based thesis management system and a \LaTeX{}-based writing template. 
A functional prototype was developed and evaluated through a mixed-methods experiment involving 24 participants (students and lecturers), comparing a control group (manual process) with an experimental group (using the D'Office solution). Quantitative metrics, including Time on Task (ToT), Task Success Rate (TSR), Formatting Compliance Score, and System Usability Scale (SUS) score, were measured, supported by qualitative data from interviews. 
The results show that the D'Office system successfully reduced the average ToT by 76\% and increased the TSR to 100\% on key tasks. 
The use of the \LaTeX{} template significantly improved the Formatting Compliance Score from 74.0 to 97.5. 
Furthermore, the D'Office system achieved an ``Excellent'' SUS score of 85.5 and received overwhelmingly positive qualitative feedback from users. 
The integrated D'Office solution is proven to be effective in enhancing the efficiency of the administrative process and the quality of thesis formatting, while providing a highly satisfactory user experience.

%The abstract is a concise and informative summary of the entire final project, essentially \catatan{covering the problem}, \catatan{objectives}, \catatan{research methods}, \catatan{results}, and \catatan{conclusions}, designed to quickly help readers understand the content of the final project and decide its relevance. This abstract must be \catatan{written in a single paragraph} with a \catatan{maximum length of 500 words}, using \catatan{Times New Roman font} \catatan{12 points}, with \catatan{single line spacing}. It is important to note that the abstract must be prepared in two languages, namely \catatan{Indonesian} and \catatan{English}, where each language version follows the same format provisions and, if possible, should be placed on one page. At the top of the abstract, the \catatan{Student's Name (without student ID)}, \catatan{Study Program}, and \catatan{Final Project Title} must be included. The bottom of each abstract (both Indonesian and English versions) must be followed by \catatan{relevant Keywords}, presented in the appropriate language (Indonesian for the Indonesian abstract, and English equivalents for the English abstract). The specific content of the abstract can be adjusted according to the respective field of study.
	\bigskip

	Keywords:
	academic information system, thesis management, \LaTeX{} template, usability evaluation, software engineering.
%    \endgroup
}

\newpage